Total Amount of Vaccinations Among Black population in the Target Zip Codes

### 2023-04-10 code/analysis_code/exploratoryanalysis.qmd
Part 4

@@

@@

@@

@@

@@

@@

@@

@@

------------------------------------------------------------------------
## Zip code: 31705

@@

@@

------------------------------------------------------------------------

@@

@@

@@

#Adding a customization title for the plot 
plot_30815_total_black_vax = plot_30815_total_black_vax + 
  ggtitle("Vaccination Totals for Black population in the 30815 Zipcode") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic"))
plot_30815_total_black_vax
```
### Turning ggplot into an interactive plot

@@

@@

@@

>>>>

### Save plot
```{r}
#save figure
ggsave(filename = here("results","31701_total_black_vax.png"), plot=plot_31701_total_black_vax)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","31705_total_black_vax.png"), plot=plot_31705_total_black_vax)
```

```{r}
plotly_31705_total_black_vax = ggplotly(plot_31705_total_black_vax)
plotly_31705_total_black_vax
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","31707_total_black_vax.png"), plot=plot_31707_total_black_vax)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","total_black_vax.png"), plot=plot_Total_black_vax)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","31701_Gender_black_vax.png"), plot=plot_Gender_black_vax)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","31705_Gender_black_vax.png"), plot=plot_Gender_black_vax_31705)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","31707_Gender_black_vax.png"), plot=plot_Gender_black_vax_31707)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","31701_Age_black_vax.png"), plot=plot_Age_black_vax)
```

@@

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","31705_Age_black_vax.png"), plot=plot_Age_black_vax)
```

@@

@@

```{r}
Age_Sum_by_month_31707 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Age_05_09 = c(275, 277, 280, 282, 284, 283),
                          Age_10_17 = c(1109, 1120, 1125, 1134, 1136, 1142),
                          Age_18_44 = c(5903, 5931, 5943, 5947, 5960, 5958), #pretty notable increase for ages 18-44 
                          Age_45_64 = c(5130, 5120, 5125, 5123, 5133, 5140),
                          Age_65Plus = c(4200, 4204, 4195, 4206, 4202, 4189))

### Converting the Age_Sum_by_month_31707 to long data in order to plot
```{r}
Age_Sum_by_month_31707_long = reshape2::melt(Age_Sum_by_month_31707, id = "Date")
```

```{r}
Age_Sum_by_month_31707_long <- Age_Sum_by_month_31707_long %>% 
  rename("Age" = "variable") %>% 
  rename("Vaccination_total" = "value")
```

### gglot2: Creating a line plot for the vaccination totals by month for the Black population by Age in the 31707 zip code

```{r}
plot_Age_black_vax = Age_Sum_by_month_31707_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Age, 
                                color = Age)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Age_black_vax = plot_Age_black_vax + 
  ggtitle("Vaccination Totals for Black population by Age in 31707") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Age_black_vax
```

### Save plot
```{r}
#save figure
ggsave(filename = here("results","31707_Age_black_vax.png"), plot=plot_Age_black_vax)
```

@@

### Separating sums by month into a data fram consisting of two variables: Date and Total #Date contains months September-February ### Total contains the vaccination totals for each month

@@

#Adding a customization title for the plot 
plot_30815_total_black_vax = plot_30815_total_black_vax + 
  ggtitle("Vaccination Totals for Black population in the 30815 Zipcode") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic"))
plot_30815_total_black_vax
```

### Save plot
```{r}
#save figure
ggsave(filename = here("results","30815_total_black_vax.png"), plot=plot_30815_total_black_vax)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","30815_Gender_black_vax.png"), plot=plot_Gender_black_vax)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","30815_Age_black_vax.png"), plot=plot_Gender_black_vax)
```

@@

## Zip code: 30907

### Loading the processed data in order to begin analysis for the 30907 zip code

```{r}
# Loading September 30907
data_location1 = here("data", "processed_data", "Zip_30907", "processed_data_30907_Sept.rds")
processed_data_30907_Sept = readRDS(data_location1)

# Loading October 30907 and joining september and october 
data_location2 = here("data", "processed_data", "Zip_30907", "processed_data_30907_Oct.rds")
processed_data_30907_Oct = readRDS(data_location2)
processed_combined <- left_join(processed_data_30907_Sept, processed_data_30907_Oct, by = c("FIPS" = "FIPS"))

# Loading November 30907
data_location3 = here("data", "processed_data", "Zip_30907", "processed_data_30907_Nov.rds")
processed_data_30907_Nov = readRDS(data_location3)
processed_combined <- left_join(processed_combined, processed_data_30907_Nov, by = c("FIPS" = "FIPS"))

# Loading December 30907
data_location4 = here("data", "processed_data", "Zip_30907", "processed_data_30907_Dec.rds")
processed_data_30907_Dec = readRDS(data_location4)
processed_combined <- left_join(processed_combined, processed_data_30907_Dec, by = c("FIPS" = "FIPS"))

# Loading January 30907
data_location5 = here("data", "processed_data", "Zip_30907", "processed_data_30907_Jan.rds")
processed_data_30907_Jan = readRDS(data_location5)
processed_combined <- left_join(processed_combined, processed_data_30907_Jan, by = c("FIPS" = "FIPS"))

# Loading February 30907
data_location6 = here("data", "processed_data", "Zip_30907", "processed_data_30907_Feb.rds")
processed_data_30907_Feb = readRDS(data_location6)
processed_combined_30907 <- left_join(processed_combined, processed_data_30907_Feb, by = c("FIPS" = "FIPS"))
```

```{r}
save_data_location = here("data", "processed_data","Zip_30907", "processed_combined_30907.rds")
saveRDS(processed_combined_30907, file = save_data_location)
```

### Dropping all variables except for total black variables in order to obtain vaccination rates of all Black population in the 30907 zip code

```{r}
processed_combined_30907_total_black = processed_combined_30907 %>% select(starts_with("total_black_vax"))
```

```{r}
#Summing each column for each month 
sum(processed_combined_30907_total_black$total_black_vax_Sept_17) 
sum(processed_combined_30907_total_black$total_black_vax_Oct_28) 
sum(processed_combined_30907_total_black$total_black_vax_Nov_24) 
sum(processed_combined_30907_total_black$total_black_vax_Dec_29) 
sum(processed_combined_30907_total_black$total_black_vax_Jan_26) 
sum(processed_combined_30907_total_black$total_black_vax_Feb_26) 
```

### Separating sums by month into a data fram consisting of two variables: Date and Total #Date contains months September-February ### Total contains the vaccination totals for each month

```{r}
Sum_by_month_30907 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Total = c(4956, 4917, 4888, 4851, 4866, 4894)) 
```

### gglot2: Creating a line plot for the vaccination totals by month for the African American population in the 30907 zip code

```{r}
plot_30907_total_black_vax = Sum_by_month_30907 %>% 
  ggplot(aes(Date, Total, group=1)) + 
  geom_point() + geom_line() + 
  scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))

#Adding a customization title for the plot 
plot_30907_total_black_vax = plot_30907_total_black_vax + 
  ggtitle("Vaccination Totals for Black population in the 30907 Zipcode") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic"))
plot_30907_total_black_vax
```

### Save plot
```{r}
#save figure
ggsave(filename = here("results","30907_total_black_vax.png"), plot=plot_30907_total_black_vax)
```

```{r}
plotly_30907_total_black_vax = ggplotly(plot_30907_total_black_vax)
plotly_30907_total_black_vax
```

## Zip code: 30907

### Loading the `processed_combined_30907.rds` file from `analysiscode.qmd`

```{r}
save_data_location = here("data", "processed_data","Zip_30907", "processed_combined_30907.rds")
processed_combined_30907 = readRDS(save_data_location)
```

### Dropping all variables except for black males and black females within 30907

```{r}
processed_combined_30907_Gender_black = processed_combined_30907 %>% select(matches("^total_(mblack|fblack)_vax"))
```

### Summing each Month variable by census tract
```{r}
#Summing for black males by month 
sum(processed_combined_30907_Gender_black$total_mblack_vax_Sept_17) 
sum(processed_combined_30907_Gender_black$total_mblack_vax_Oct_28) 
sum(processed_combined_30907_Gender_black$total_mblack_vax_Nov_24) 
sum(processed_combined_30907_Gender_black$total_mblack_vax_Dec_29) 
sum(processed_combined_30907_Gender_black$total_mblack_vax_Jan_26) 
sum(processed_combined_30907_Gender_black$total_mblack_vax_Feb_26)

#summing for black females by month 
sum(processed_combined_30907_Gender_black$total_fblack_vax_Sept_17) 
sum(processed_combined_30907_Gender_black$total_fblack_vax_Oct_28) 
sum(processed_combined_30907_Gender_black$total_fblack_vax_Nov_24) 
sum(processed_combined_30907_Gender_black$total_fblack_vax_Dec_29) 
sum(processed_combined_30907_Gender_black$total_fblack_vax_Jan_26) 
sum(processed_combined_30907_Gender_black$total_fblack_vax_Feb_26) 
```

```{r}
Gender_Sum_by_month_30907 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Male_Total = c(1947, 1943, 1926, 1900, 1913, 1919),
                          Female_Total = c(3009, 2974, 2962, 2951, 2953, 2975))
```

### Converting the Gender_Sum_by_month_30907 to long data in order to plot
```{r}
Gender_Sum_by_month_30907_long = reshape2::melt(Gender_Sum_by_month_30907, id = "Date")
```

```{r}
Gender_Sum_by_month_30907_long <- Gender_Sum_by_month_30907_long %>% 
  rename("Gender" = "variable") %>% 
  rename("Vaccination_total" = "value")
```

### gglot2: Creating a line plot for the vaccination totals by month for the Black population by gender in the 30907 zip code

```{r}
plot_Gender_black_vax = Gender_Sum_by_month_30907_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Gender, 
                                color = Gender)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Gender_black_vax = plot_Gender_black_vax + 
  ggtitle("Vaccination Totals for Black population by Gender in 30907") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Gender_black_vax
```

### Save plot
```{r}
#save figure
ggsave(filename = here("results","30907_Gender_black_vax.png"), plot=plot_Gender_black_vax)
```

## Zip code: 30907

### Loading the `processed_combined_30907.rds` file from `analysiscode.qmd`

```{r}
save_data_location = here("data", "processed_data","Zip_30907", "processed_combined_30907.rds")
processed_combined_30907 = readRDS(save_data_location)
```

### Dropping all variables except for black age groups within 30907

```{r}
processed_combined_30907_Age_black = processed_combined_30907 %>% 
  select(starts_with("total_05_09"), starts_with("total_10_17"), starts_with("total_18_44"), starts_with("total_45_64"), starts_with("total_65Plus"))
```

### Summing each Month variable by age group by month
```{r}
#Summing for ages 5-9 by month 
sum(processed_combined_30907_Age_black$total_05_09_vax_Sept_17) 
sum(processed_combined_30907_Age_black$total_05_09_vax_Oct_28) 
sum(processed_combined_30907_Age_black$total_05_09_vax_Nov_24) 
sum(processed_combined_30907_Age_black$total_05_09_vax_Dec_29) 
sum(processed_combined_30907_Age_black$total_05_09_vax_Jan_26) 
sum(processed_combined_30907_Age_black$total_05_09_vax_Feb_26)

#Summing for ages 10-17 by month 
sum(processed_combined_30907_Age_black$total_10_17_vax_Sept_17) 
sum(processed_combined_30907_Age_black$total_10_17_vax_Oct_28) 
sum(processed_combined_30907_Age_black$total_10_17_vax_Nov_24) 
sum(processed_combined_30907_Age_black$total_10_17_vax_Dec_29) 
sum(processed_combined_30907_Age_black$total_10_17_vax_Jan_26) 
sum(processed_combined_30907_Age_black$total_10_17_vax_Feb_26)

#Summing for ages 18-44 by month 
sum(processed_combined_30907_Age_black$total_18_44_vax_Sept_17) 
sum(processed_combined_30907_Age_black$total_18_44_vax_Oct_28) 
sum(processed_combined_30907_Age_black$total_18_44_vax_Nov_24) 
sum(processed_combined_30907_Age_black$total_18_44_vax_Dec_29) 
sum(processed_combined_30907_Age_black$total_18_44_vax_Jan_26) 
sum(processed_combined_30907_Age_black$total_18_44_vax_Feb_26)

#Summing for ages 45-64 by month 
sum(processed_combined_30907_Age_black$total_45_64_vax_Sept_17) 
sum(processed_combined_30907_Age_black$total_45_64_vax_Oct_28) 
sum(processed_combined_30907_Age_black$total_45_64_vax_Nov_24) 
sum(processed_combined_30907_Age_black$total_45_64_vax_Dec_29) 
sum(processed_combined_30907_Age_black$total_45_64_vax_Jan_26) 
sum(processed_combined_30907_Age_black$total_45_64_vax_Feb_26)

#Summing for ages 65+ by month 
sum(processed_combined_30907_Age_black$total_65Plus_vax_Sept_17) 
sum(processed_combined_30907_Age_black$total_65Plus_vax_Oct_28) 
sum(processed_combined_30907_Age_black$total_65Plus_vax_Nov_24) 
sum(processed_combined_30907_Age_black$total_65Plus_vax_Dec_29) 
sum(processed_combined_30907_Age_black$total_65Plus_vax_Jan_26) 
sum(processed_combined_30907_Age_black$total_65Plus_vax_Feb_26)

```{r}
Age_Sum_by_month_30907 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Age_05_09 = c(244, 239, 241, 236, 240, 242),
                          Age_10_17 = c(1344, 1358, 1357, 1341, 1343, 1335),
                          Age_18_44 = c(9203, 9217, 9238, 9245, 9253, 9246),
                          Age_45_64 = c(6740, 6700, 6667, 6626, 6617, 6624),
                          Age_65Plus = c(6632, 6633, 6639, 6635, 6633, 6623))

### Converting the Age_Sum_by_month_30907 to long data in order to plot
```{r}
Age_Sum_by_month_30907_long = reshape2::melt(Age_Sum_by_month_30907, id = "Date")
```

```{r}
Age_Sum_by_month_30907_long <- Age_Sum_by_month_30907_long %>% 
  rename("Age" = "variable") %>% 
  rename("Vaccination_total" = "value")
```

### gglot2: Creating a line plot for the vaccination totals by month for the Black population by Age in the 30907 zip code

```{r}
plot_Age_black_vax = Age_Sum_by_month_30907_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Age, 
                                color = Age)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Age_black_vax = plot_Age_black_vax + 
  ggtitle("Vaccination Totals for Black population by Age in 30907") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Age_black_vax
```

### Save plot
```{r}
#save figure
ggsave(filename = here("results","30907_Age_black_vax.png"), plot=plot_Age_black_vax)
```
